\section{Conclusion and Future Works}

%$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$
%Paragraph 1:Spark Scalability의 연구에 대한 설명
%$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$
\ifkor
We proposed a Docker container-based partitioning method for Apache
Spark scalability on scale-up server.
To eliminate GC and remote memory access, we divided per-socket and best-fit partitioning.
Evaluation results(Word Count, Naive Basian, Grep and K-means) reveal
that Docker-container method has substantial performance up to 1.7 times
compared to existing solutions.
\newline\\
\noindent
\textbf{Future Directions.} Our future directions are:
\begin{itemize}
\item \textbf{Implementing the proof-of-concept architecture.} This paper shows manually
partitioning method, so we will implement the Docker-container-based
partitioning method.
%However, many of science applications or big data analytics 
%may reuse similar workloads, so training phase for finding the best-fit
%partitioning can be a superior solution in a way similar to compiler-based
% auto-tuner~\cite{Ansel2014OEF}.
\item \textbf{Solving the straggler tasks problem.} straggler tasks
significantly extend job completion times.
To mitigate this problem, we may use dynamic resource allocation solution in
Docker to maximized CPU utilization.
\end{itemize}

\section{Acknowledgments}
This work was supported by Institute for Information \& communications Technology 
Promotion (IITP) grant funded by the Korea government (MSIP) (No. B010-16-0644)

\else

\fi
